---
title: "Twitter"
date: '2017-10-31T21:28:43-05:00'
description: ''
draft: no

keywords: ''
slug: twitter
categories:
- ''
- ''
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)

```

```{r}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(lubridate)
library(here)
library(skimr)
library(janitor)
library(httr)
library(readxl)
library(vroom)
library(DescTools)
```

## Twitter usage by education level

Can we estimate the *population* proportion of Twitter users by education level in 2016?

Yes, statistically it is viable to extrapolate a population (split) of users from a sufficiently large sample set. There are requirements that have to be met for this to work, such as non-overlapping confidence intervals, but generally it is possible to estimate the population. In the same way that election polls do not ask the whole country but just a very small group of people, these techniques can be applied to other measures.
Below you can find a code for mean point estimation on the given sample:

```{r, read_gss_data, cache=TRUE}

gss <- read_csv(here::here("data", "smallgss2016.csv"), 
                na = c("", "Don't know",
                       "No answer", "Not applicable"))

```
```{r}
gss <- gss %>% 
  mutate(degree = factor(degree, levels = c("Lt high school", "High school", "Junior college", "Bachelor", "Graduate"), ordered = TRUE))

gss %>% 
  filter(degree != "NA") %>% 
  filter(twitter != "NA") %>% 
  group_by(degree) %>% 
  summarize(prop_deg = sum(twitter == "Yes")/n())
```



There are 5 education levels in variable `degree` which, in ascending order of years of education, are Lt high school, High school, Junior college, Bachelor, Graduate. 

- Turn `degree` from a character variable into a factor variable. Make sure the order is the correct one and that levels are not sorted alphabetically which is what R by default does. 

```{r}

gss <- gss %>% 
  mutate(degree = factor(degree, levels = c("Lt high school", "High school", "Junior college", "Bachelor", "Graduate"), ordered = TRUE))

```

- Create a  new variable, `bachelor_graduate` that is *Yes* if the respondent has either a `Bachelor` or `Graduate` degree. As before, if the recorded value for either was NA, the value in your new variable should also be NA.

```{r}

gss <- gss %>% 
  mutate(bachelor_graduate = case_when(
    degree == "Bachelor" | degree == "Graduate" ~ "Yes",
    degree == "NA" ~ NA_character_,
    TRUE ~ "No"
  ))

```

- Calculate the proportion of `bachelor_graduate` who do (Yes) and who don't (No) use twitter. 

```{r}

tw_total <- gss %>% 
  filter(twitter != "NA") %>% 
  filter(bachelor_graduate == "Yes") %>%
  count()

tw_yes <- gss %>% 
  filter(bachelor_graduate == "Yes", twitter == "Yes") %>% 
  count()

prop_yes <- (tw_yes/tw_total*100)
prop_no <- (1-tw_yes/tw_total)*100

paste0("The proportion of Bachelors and Graduates using Twitter is ", round(prop_yes, 2), "%")
paste0("The proportion of Bachelors and Graduates not using Twitter is ", round(prop_no, 2), "%")

```

- Using the CI formula for proportions, we construct two 95% CIs for `bachelor_graduate` vs whether they use (Yes) and don't (No) use twitter.

```{r}

yes_ci <- BinomCI(as.integer(tw_yes), as.integer(tw_total), conf.level = 0.95)

no_ci <- BinomCI(as.integer(tw_total - tw_yes), as.integer(tw_total), conf.level = 0.95)

paste0("95% CI for usage of Twitter among Bachelors and Graduates is between ", round(yes_ci[2],2), " and ",
       round(yes_ci[3],2))

paste0("95% CI for Bachelors and Graduates proportion not using Twitter is between ", round(no_ci[2],2), " and ",
       round(no_ci[3],2))

```


- Do these two Confidence Intervals overlap?

No, as estimated values are significantly different (if the proportion of users was around 0.5 there would be a higher chance of overlap) and the sample size is large (making the CIs quite narrow), there is no overlap.

